Production-maintenance scheduling in complex machinery

### 2024-10-24 Paper.tex
Added results and quick analysis

%todo note
\usepackage{ulem}
\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}
\newcommand{\jpp}[1]{{\color{teal}#1}}
\newcommand{\jppC}[1]{\todo[backgroundcolor=teal!25,bordercolor=teal]{#1}}
\normalem % removing underscore in loops and ifs
% \newcommand{\qmax}{{\textsf{q$^\textsf{max}$}}}

@@

\keywords{Production-maintenance scheduling \and Dantzig-Wolfe decomposition \and MINLP \and Resource allocation}
\end{abstract}
%
%
%
\todo[inline]{KB: to make git diffs more meaningful, it helps to write each sentence on its own line. You don't have to change everything now, but you can change this in the parts that you edit anyway. JD@KB:Done.}
\todo[inline]{KB: your use of commas is often excessive; it might come from a difference between punctuation rules in your language and English. I am removing some unneeded commas as I go, but this is something you might want to watch out for generally.}
\label{sec:intro}
\section{Introduction}

@@

    This work was funded by the Portuguese Foundation for Science and Technology - FCT under ????, and by Zuse Institute Berlin - ZIB.

@@

\section{Dantzig-Wolfe Reformulation}
\label{sec:DW}
    The formulation above exhibits a block diagonal structure with a set of complicating constraints. 
    These are Constraints~\eqref{con:satisfy_demand}, requiring that the demand must be satisfied, while the blocks are composed of the constraints describing the functioning of the independent machines. 
    Dantzig-Wolfe decomposition is a method for solving problems with these attributes~\cite{Decomposition_Principle_for_Linear_Programs}. 
    The nonlinearities in the formulation will appear in the pricing problem, thus not directly interfering with the algorithm. 
    Example of other works with nonlinear pricing problems can be found in~\cite{Exact_Methods_for_Recursive_Circle_Packing, Security_Constrained_Economic_Dispatch_Using_Nonlinear_Dantzig-Wolfe_Decomposition, Branch-and-price_for_a_class_of_nonconvex_mixed-integer_nonlinear_programs}.

@@

This reformulation is solved with column generation, which will provide new production-maintenance patterns for each of the different sets of machines, looking for the ones with the lowest reduced cost. 
The dual variables from constraints~\eqref{con:lambda_production_demand} will incentivize solutions with a higher production, while the maintenance cost will prevent solutions with too many maintenance actions. 
The generation of new patterns is obtained by the pricing problem below.

@@

As the subproblems can be very difficult when solved exactly, we will use the results of the heuristic described in Section~\ref{sec:heuristics} to decide the order in which they should be solved. 
Subproblems with a more promising heuristic result will be solved first.
After getting a column with a negative reduced cost, we advance to the next iteration in order to get more up-to-date dual values.
As the master problem is not difficult, in contrast with the pricing problem, using the best possible dual values is preferable.

@@

\subsubsection{Dual bound} ?????? WORK IN PROGRESS ?????
The following is a dual bound for the master problem: ??? WHAT IS THE NAME? NEED REFERENCE ???
$$c^\ast_{\text{RMP}} + \sum_{z \in \mathcal{Z}}|\mathcal{Z}_z|\cdot min(0,w_{\text{PP}_n}) \leq c^\ast_{\text{MP}}$$,

where $c^\ast_{\text{RMP}}$ is the optimal objective of the restricted master problem, $c^\ast_{\text{MP}}$ is the optimal objective of the master problem, and $w$ is a valid dual bound for pricing problem $n$.

\subsubsection{Parallelism}

?????? I WILL MOST LIKELY NOT BE IMPLEMENTING THIS

In decomposition approaches, solving the different subproblems in parallel can yield large speedups (in the order of $T/t$, where T is the time to solve all subproblems, and t is the time to solve the most difficult subproblem). 
While it is also possible to use parallelism to increase the speed of the compact formulation (see~\cite{Assessing_the_Effectiveness_of_(Parallel)_Branch-and-bound_Algorithms} for a review), this would take considerably more effort, both from a technical and a theoretical perspective. 
For this reason, it is our understanding that applying parallelism only to the decomposition approach is not unfair.

\section{Heuristic \& Simplifications}
\label{sec:heuristics}

@@

\todo[inline]{KB: I find this paragraph to be too vague to be helpful to the reader. You could clarify/expand a bit.}
For that reason, we developed a heuristic that tries to deal with this. 
It is applied to the column generation process, and remains applicable if it is used to initialize the RMP (in other words, when solving the Farkas iterations).

@@

\subsection{Simplifications}

\todo[inline]{KB: this is still what you are doing in the implementation, right? I would include this as a paragraph or two in the extended formulation implementation section, but I agree that this doesn't seem to be big enough for a separate subsection}

PROBABLY I'LL REMOVE THIS SUBSECTION

This model may quickly become very large, depending on the number of periods being considered, but even for average-sized instances, it can be quite difficult to solve.

To cope with this, we assume that there are different time periods for production and maintenance decisions. 
For example, while production decisions are made every hour, maintenance might be planned on a biyearly basis. 
This forces minor modifications to the formulations, and some more significant ones, as the constraints that combine both $y$ and $x$ variables (like~\eqref{con:component_degradation}) need to use the proper indices.

Despite having a big impact on the tractability of the models, this simplification also falls in line with real-world applications, since maintenance decisions are naturally made on a much more granular scale than production decisions.

@@

 The instances were randomly generated. 
 They are divided by the number of time periods (either $10$, $20$, or $50$), by the number of machines (with some being identical), and they can have ``high'' or ``low'' complexity, meaning that the corresponding machines will have a higher or lower number of components with more or less interaction between them. 
 The complexity of the components also affects the amount of nonlinearity in the model. 
 For each of these combinations, we generate $10$ different instances.

 It is easy to create instances that favor each of the models, as having more or less identical machines favors the extended or the compact formulation respectively. 
 For this reason, we have opted for creating three sets of instances, with one of them having several identical machines (one group of $20$ machines), one other having many dissimilar machines ($4$ groups of $2$), and an intermediate set (one group of $5$ and one group of $2$). %Thus our test set has $10\cdot 3\cdot 2\cdot 3 = 180$ different tests.

\todo[inline]{KB: please double check that this is indeed what you meant: I rephrased the sentence. JD@KB: Done. Rephrased a bit as well.}
The varying combinations of time periods, complexity and machine groups yield $10\cdot 3\cdot 2\cdot 3 = 180$ different instances.

For every instance, we ran three formulations: the compact formulation, the extended formulation with exact pricing, and the extended formulation with heuristic pricing. 
In the result subsection represented by ``Compact'', ``DW'', and ``DW+PF'' respectively.\todo{KB: specify how these formulations are denoted in the tables. JD@KB: Done.}

@@

The experiments were run on two 6-Core Intel Core i7 with 64 GB running at 3.20GHz with a 30 minute time limit.
The models were solved with the SCIP solver, version 9.0.0~\cite{scip9.0}. 
For the implementation, we used SCIP's Python interface, PySCIPOpt~\cite{PySCIPOPT}, version 5.0. Some scripts (most importantly visualization with Matplotlib~\cite{matplotlib}) were implemented in Python version 3.11.4.

@@

???
FIGURES $>$ TABLES?
HOW MANY INSTANCES?
WHAT TO VARY?

\begin{table}[!htb]
  \caption{Comparing effect of time}

  \scalebox{0.9}{
  \begin{minipage}{.5\linewidth}
    \caption{Results for $\mathcal{T} = 20$}
    \centering
      \begin{tabular}{|c|c|c|c|c|c|}
        \hline
        Model & $\mathcal{N}$ & Complexity & Time(s) & Gap (\%) \\
        \hline
        Compact & ??? & ??? & ??? & ??? \\
        DW & ??? & ??? & ??? & ??? \\
        DW + PF & ??? & ??? & ??? & ??? \\
        \hline
      \end{tabular}
  \end{minipage}
  }
  \scalebox{0.9}{
  \begin{minipage}{.5\linewidth}
    \centering
      \caption{Results for $\mathcal{T} = 50$}
      \begin{tabular}{|c|c|c|c|c|c|}
        \hline
        Model & $\mathcal{N}$ & Complexity & Time(s) & Gap (\%) \\
        \hline
        Compact & ??? & ??? & ??? & ??? \\
        DW & ??? & ??? & ??? & ??? \\
        DW + PF & ??? & ??? & ??? & ??? \\
        \hline
      \end{tabular}
  \end{minipage} 
  }
\end{table}

\begin{table}[!htb]
  \caption{Comparing effect of different machines}

  \scalebox{0.9}{
  \begin{minipage}{.5\linewidth}
    \caption{Results for $\mathcal{N} = ???$}
    \centering
    \begin{tabular}{|c|c|c|c|c|c|}
      \hline
        Model & $\mathcal{T}$ & Complexity & Time(s) & Gap (\%) \\
        \hline
        Compact & ??? & ??? & ??? & ??? \\
        DW & ??? & ??? & ??? & ??? \\
        DW + PF & ??? & ??? & ??? & ??? \\
        \hline
      \end{tabular}
  \end{minipage}
  }
  \scalebox{0.9}{
  \begin{minipage}{.5\linewidth}
    \centering
      \caption{Results for $\mathcal{N} = ???$}
      \begin{tabular}{|c|c|c|c|c|c|}
        \hline
        Model & $\mathcal{T}$ & Complexity & Time(s) & Gap (\%) \\
        \hline
        Compact & ??? & ??? & ??? & ??? \\
        DW & ??? & ??? & ??? & ??? \\
        DW + PF & ??? & ??? & ??? & ??? \\
        \hline
      \end{tabular}
  \end{minipage} 
  }
\end{table}

\todo[inline]{KB: don't you already have different complexities in the previous tables? JD@KB: Yeah, I still need to think how I want to present the results...}
\begin{table}[!htb]
  \caption{Comparing effect of machine complexity}

  \begin{minipage}{.5\linewidth}
    \caption{Results for low complexity}
    \centering
      \begin{tabular}{|c|c|c|c|c|c|}
        \hline
        Model & $\mathcal{N}$ & $\mathcal{T}$ & Time(s) & Gap (\%) \\
        \hline
        Compact & ??? & ??? & ??? & ??? \\
        DW & ??? & ??? & ??? & ??? \\
        DW + PF & ??? & ??? & ??? & ??? \\
        \hline
      \end{tabular}
  \end{minipage}
  \begin{minipage}{.5\linewidth}
    \centering
      \caption{Results for high complexity}
      \begin{tabular}{|c|c|c|c|c|c|}
        \hline
        Model & $\mathcal{N}$ & $\mathcal{T}$ & Time(s) & Gap (\%) \\
        \hline
        Compact & ??? & ??? & ??? & ??? \\
        DW & ??? & ??? & ??? & ??? \\
        DW + PF & ??? & ??? & ??? & ??? \\
        \hline
      \end{tabular}
  \end{minipage} 
\end{table}

As expected, the decomposition approaches appear advantageous in comparison to the compact model when increasing the number of identical machines. On the other hand, having more machines increases the number of pricing problems, and longer time-horizons increase their difficulty, so the compact formulation seems better suited for these instances.

An increase in machine complexity also increases the difficulty of the pricing problems....

@@

SLIGHTLY OUTDATED

This article presented a MINLP for a general production-maintenance scheduling problem. 
Besides the compact model, we also developed a Dantzig-Wolfe reformulation, and an additional heuristic due to the model's difficulty.

    The model is able to solve multiple medium-sized instances to optimality, but on larger instances, the difficulty grows rapidly. 
    The heuristic has trouble reaching optimality but can obtain good solutions very quickly, and in larger instances, it even gets better results that the original model. 
    These results leave us optimistic that we can decrease the granularity of small and medium-sized instances, and still obtain good solutions.% We based the data characterizing a power transformer on the information we could discover in the literature~\cite{cigre445}, due to the lack of quality real-world data available.

    The heuristic proved to be a good complement to exact pricing.
    Besides the comments at the end of the heuristic's description, we are considering taking better advantage of how fast the heuristic is.
    Our idea is doing multiple iterations of the heuristic with different production vectors, while adding benders-like optimality and feasibility cuts, which should provide significantly better columns.

  A different extended formulation shows promising results, by reducing the number of costly pricing rounds. 
  The idea is to generate maintenance patterns and production patterns (patterns being a concrete assignment to the corresponding variables) in different pricing problems. 
  The formulation we arrived at requires more theory than this one, as it requires the simultaneous generation of columns and rows. 
  See~\cite{Simultaneous_column-and-row_generation} for more details on column-and-row generation.

  On the modeling side, more than one type of maintenance action can make the model more interesting. 
  It increases its difficulty, but it also makes it more realistic, as complete replacement of a component is usually not the only option. 
  The model can also become more general. 
  For example, there might be non-critical components that may be maintained while still allowing for some production of the machine.
   Another example is the production upper bound in Constraints\eqref{con:production_limit}, which might depend not only on the condition of individual components, but also on the joint condition of multiple components.

>>>>

%todo note
\usepackage{ulem}
\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}
%\newcommand{\jpp}[1]{{\color{teal}#1}}
%\newcommand{\jppC}[1]{\todo[backgroundcolor=teal!25,bordercolor=teal]{#1}}

\normalem % removing underscore in loops and ifs
% \newcommand{\qmax}{{\textsf{q$^\textsf{max}$}}}

@@

\keywords{Production-maintenance scheduling \and Dantzig-Wolfe decomposition \and MINLP \and Resource allocation \and Branch-and-Price}
\end{abstract}
%
%
%
\todo[inline]{KB: to make git diffs more meaningful, it helps to write each sentence on its own line. You don't have to change everything now, but you can change this in the parts that you edit anyway. JD@KB:Done.}
\todo[inline]{KB: your use of commas is often excessive; it might come from a difference between punctuation rules in your language and English. I am removing some unneeded commas as I go, but this is something you might want to watch out for generally.}
\label{sec:intro}
\section{Introduction}

@@

    This work was funded by the Portuguese Foundation for Science and Technology - FCT with the scholarship 2023.00422.BD, and by Zuse Institute Berlin - ZIB.

@@

\section{Dantzig-Wolfe Reformulation}
\label{sec:DW}
    The formulation above exhibits a block diagonal structure with a set of complicating constraints. 
    These are Constraints~\eqref{con:satisfy_demand}, requiring that the demand must be satisfied, while the blocks are composed of the constraints describing the functioning of the independent machines. 
    Dantzig-Wolfe decomposition allows the reformulation of problems with these attributes~\cite{Decomposition_Principle_for_Linear_Programs}, allowing them to be solved with Branch-and-Price. 
    Recently, Desrosiers et al. published a book on Branch-and-Price~\cite{Branch-and-Price}, where one might get a better understanding of the methods mentioned in this paper.
    The nonlinearities in the formulation will appear in the pricing problem, thus not directly interfering with the algorithm. 
    Example of other works with nonlinear pricing problems can be found in~\cite{Exact_Methods_for_Recursive_Circle_Packing, Security_Constrained_Economic_Dispatch_Using_Nonlinear_Dantzig-Wolfe_Decomposition, Branch-and-price_for_a_class_of_nonconvex_mixed-integer_nonlinear_programs}.

@@

This reformulation is solved with column generation, which uses pricing problems to provide new production-maintenance patterns for each of the different sets of machines, with the objective of finding the ones with the minimum reduced cost.
The dual variables from constraints~\eqref{con:lambda_production_demand} will incentivize solutions with a higher production, while the maintenance cost will prevent solutions with too many maintenance actions. 
The generation of new patterns is obtained by the pricing problem below.

@@

As the subproblems can be very difficult when solved exactly, we will use the results of the heuristic described in Section~\ref{sec:heuristics} to decide the order in which they should be solved. 
Subproblems with a more promising heuristic result will be solved first.
If the negative reduced cost columns obtained in this manner are added to the RMP, then we call the model ``DW+PF'' in Section~\ref{sec:results}, otherwise ``DW''.

@@

  \vspace{1em}

  As the branching decisions are added to the local restricted master problems, the corresponding duals will also influence the reduced cost of the remaining columns.
  It is then necessary to incorporate them into the objective function of the pricing problem, which becomes

  \begin{mini!}|l|[3]
  {x,y}{C^\intercal x - \pi^\intercal y - \pi_0 - \gamma x}
  {}{}
  \end{mini!}

\subsubsection{Lagrangian bound}
The following is a well known dual bound for the master problem:

$$c^\ast_{\text{RMP}} + \sum_{z \in \mathcal{Z}}|\mathcal{Z}_z|\cdot \max(0,w_z) \leq c^\ast_{\text{MP}},$$

where $c^\ast_{\text{RMP}}$ is the optimal objective of the restricted master problem, $c^\ast_{\text{MP}}$ is the optimal objective of the master problem, and $w_z$ is a valid dual bound for pricing problem $z$.

The minimum reduced cost indicates the largest improvement in the objective per unit increase of the corresponding variable (which may not be feasible).
Thus, choosing to add the columns associated to the minimum reduced cost of each subproblem in the RMP yields an upper bound on the improvement of the current iteration. \\
As not all iterations are solved to optimality, it is useful that this remains true for any valid lower bound.

% \subsubsection{Parallelism}

% ?????? I WILL MOST LIKELY NOT BE IMPLEMENTING THIS

% In decomposition approaches, solving the different subproblems in parallel can yield large speedups (in the order of $T/t$, where T is the time to solve all subproblems, and t is the time to solve the most difficult subproblem). 
% While it is also possible to use parallelism to increase the speed of the compact formulation (see~\cite{Assessing_the_Effectiveness_of_(Parallel)_Branch-and-bound_Algorithms} for a review), this would take considerably more effort, both from a technical and a theoretical perspective. 
% For this reason, it is our understanding that applying parallelism only to the decomposition approach is not unfair.

\section{Pricing problem heuristics}
\label{sec:heuristics}

@@

\todo[inline]{KB: I find this paragraph to be too vague to be helpful to the reader. You could clarify/expand a bit.}
For that reason, we developed a new heuristic that tries to quickly create columns, which can be used for solving the Farkas' iterations (to initialize the RMP and to fix local infeasibilities), or to add columns with a negative reduced cost.
As referenced in Section~\ref{sec:implementation}, this heuristic may also be helpful in an exact setting, since it can provide an idea of which subproblems are more promissing and should be solved first.

@@

% \subsection{Simplifications}

% \todo[inline]{KB: this is still what you are doing in the implementation, right? I would include this as a paragraph or two in the extended formulation implementation section, but I agree that this doesn't seem to be big enough for a separate subsection}

% PROBABLY I'LL REMOVE THIS SUBSECTION

% This model may quickly become very large, depending on the number of periods being considered, but even for average-sized instances, it can be quite difficult to solve.

% To cope with this, we assume that there are different time periods for production and maintenance decisions. 
% For example, while production decisions are made every hour, maintenance might be planned on a biyearly basis. 
% This forces minor modifications to the formulations, and some more significant ones, as the constraints that combine both $y$ and $x$ variables (like~\eqref{con:component_degradation}) need to use the proper indices.

% Despite having a big impact on the tractability of the models, this simplification also falls in line with real-world applications, since maintenance decisions are naturally made on a much more granular scale than production decisions.

@@

 \todo[inline]{Explain how you generated the instances (what are the nonlinearities?)}
 The instances were randomly generated. 
 They are divided by the number of time periods (either $10$ or $20$), by the number of machines (with some being identical), and they can have ``high'' or ``low'' complexity, meaning that the corresponding machines will have a higher or lower number of components with more or less interaction between them. 
 The complexity of the components also affects the amount of nonlinearity in the model. 
 For each of these combinations, we generate $5$ different instances.

 Functions $f$ and $g$ from the compact formulation and the pricing problem can randomly be linear, polynomial (with a maximum exponent of $4$ for $f$ and $5$ for $g$), or exponential.

 It is easy to create instances that favor each of the models, as having more or less identical machines favors the extended or the compact formulation respectively. 
 For this reason, we have opted for creating two sets of instances, with one of them having several identical machines (one group of $20$ machines), and another having two medium-sized groups of identical machines ($2$ sets of $10$ each).

\todo[inline]{KB: please double check that this is indeed what you meant: I rephrased the sentence. JD@KB: Done. Rephrased a bit as well.}
The varying combinations of time periods, complexity and machine groups yield $2\cdot 2\cdot 2\cdot 5 = 40$ different instances.

For every instance, we ran three formulations: the compact formulation, the extended formulation with exact pricing, and the extended formulation with heuristic pricing (which resorts to exact pricing whenever the heuristic could not find a negative reduced cost column). 
In the result subsection represented by ``Compact'', ``DW'', and ``DW+PF'' respectively.\todo{KB: specify how these formulations are denoted in the tables. JD@KB: Done.}

@@

The experiments were run on two 6-Core Intel Core i7 with 64 GB running at 3.20GHz with a 30 minute time limit.
The models were solved with the SCIP solver, version 9.1.0~\cite{scip9.0}. 
For the implementation, we used SCIP's Python interface, PySCIPOpt~\cite{PySCIPOPT}, version 5.1.1. Some scripts (most importantly visualization with Matplotlib~\cite{matplotlib}) were implemented in Python version 3.11.4.

@@

% ???
% FIGURES $>$ TABLES?
% HOW MANY INSTANCES?
% WHAT TO VARY?

\begin{tabular}{|c|c|c|c|c|c|}
  \hline
  DW  & Trivial & Easy & Medium & Hard & Impossible\\
  \hline
  Optimal    & 6     & 0     & 0     & -    & -\\
  Timeout    & -     & -     & -     & 12   & 7\\
  Infeasible & 12    & 2     & 1     & -    & -\\
  Gap        & 0     & 0     & 0     & 1275 & -\\
  N\_cols    & 408   & 258   & 342   & 7212 & 2240\\
  Total time & 19.46 & 54.86 & 81.31 & -    & -\\
  \hline
\end{tabular}

\begin{tabular}{|c|c|c|c|c|c|}
  \hline
  DW+PF & Trivial & Easy & Medium & Hard & Impossible\\
  \hline
  Optimal    & 6     & 0     & 0      & -    & -\\
  Timeout    & -     & -     & -      & 13   & 5\\
  Infeasible & 12    & 2     & 2      & -    & -\\
  Gap        & 0     & 0     & 0      & 1576 & -\\
  N\_cols    & 461   & 216   & 963    & 8809 & 1714\\
  Total time & 18.42 & 35.84 & 242.76 & -    & -\\
  \hline
\end{tabular}

\begin{tabular}{|c|c|c|c|c|c|}
  \hline
  Compact & Trivial & Easy & Medium & Hard & Impossible\\
  \hline
  Optimal    & 7    & 1     & 1      & -      & -\\
  Timeout    & -    & -     & -      & 10     & 9\\
  Infeasible & 9    & 1     & 2      & -      & -\\
  Gap        & 0    & 0     & 0      & 2538.7 & -\\
  Total time & 5.36 & 83.46 & 540.65 & -      & -\\
  \hline
\end{tabular}

\vspace{1em}

The compact model is the one that most often could not find a feasible solution in the allocated time, contrasting with heuristic pricing (9 vs 5 instances).\\

The decomposition approaches were better at proving infeasibilities, likely due to Farkas' Pricing.
Both managed to find 12 infeasible instances trivially, while the compact model could only do so for 9 of them.
In total, heuristic pricing proved 16 instances to be infeasible, while Compact could only do it for 12.

The compact formulation found more optimal solutions for the given time limit.
A total of 9 instances (7 trivial, 1 easy, 1 medium) were solved to optimality, against 6 trivial ones by the decomposition approaches.

With an average gap of 106.25\%, the DW algorithm performed the best on the instances that hit the time limit, when comparing with DW+PF (average gap of 121.23\%), and Compact (average gap of 253.87\%).

It is our understanding that the heuristic was overall a good addition to exact pricing.
Heuristic pricing reduced the number of instances for which no solution could be found (from 7 to 5), and could prove infeasibility for an extra instance.
It also does not seem to have added many more columns to the RMP, potentially indicating that more work could increase its effectiveness in finding good columns.\\

From this analysis, we conclude that the compact formulation yielded the worst results, while the decomposition approach with heuristic pricing the best.

% \begin{table}[!htb]
%   \caption{Comparing effect of time}

%   \scalebox{0.9}{
%   \begin{minipage}{.5\linewidth}
%     \caption{Results for $\mathcal{T} = 20$}
%     \centering
%       \begin{tabular}{|c|c|c|c|c|c|}
%         \hline
%         Model & $\mathcal{N}$ & Complexity & Time(s) & Gap (\%) \\
%         \hline
%         Compact & ??? & ??? & ??? & ??? \\
%         DW & ??? & ??? & ??? & ??? \\
%         DW + PF & ??? & ??? & ??? & ??? \\
%         \hline
%       \end{tabular}
%   \end{minipage}
%   }
%   \scalebox{0.9}{
%   \begin{minipage}{.5\linewidth}
%     \centering
%       \caption{Results for $\mathcal{T} = 50$}
%       \begin{tabular}{|c|c|c|c|c|c|}
%         \hline
%         Model & $\mathcal{N}$ & Complexity & Time(s) & Gap (\%) \\
%         \hline
%         Compact & ??? & ??? & ??? & ??? \\
%         DW & ??? & ??? & ??? & ??? \\
%         DW + PF & ??? & ??? & ??? & ??? \\
%         \hline
%       \end{tabular}
%   \end{minipage} 
%   }
% \end{table}

% \begin{table}[!htb]
%   \caption{Comparing effect of different machines}

%   \scalebox{0.9}{
%   \begin{minipage}{.5\linewidth}
%     \caption{Results for $\mathcal{N} = ???$}
%     \centering
%     \begin{tabular}{|c|c|c|c|c|c|}
%       \hline
%         Model & $\mathcal{T}$ & Complexity & Time(s) & Gap (\%) \\
%         \hline
%         Compact & ??? & ??? & ??? & ??? \\
%         DW & ??? & ??? & ??? & ??? \\
%         DW + PF & ??? & ??? & ??? & ??? \\
%         \hline
%       \end{tabular}
%   \end{minipage}
%   }
%   \scalebox{0.9}{
%   \begin{minipage}{.5\linewidth}
%     \centering
%       \caption{Results for $\mathcal{N} = ???$}
%       \begin{tabular}{|c|c|c|c|c|c|}
%         \hline
%         Model & $\mathcal{T}$ & Complexity & Time(s) & Gap (\%) \\
%         \hline
%         Compact & ??? & ??? & ??? & ??? \\
%         DW & ??? & ??? & ??? & ??? \\
%         DW + PF & ??? & ??? & ??? & ??? \\
%         \hline
%       \end{tabular}
%   \end{minipage} 
%   }
% \end{table}

% \todo[inline]{KB: don't you already have different complexities in the previous tables? JD@KB: Yeah, I still need to think how I want to present the results...}
% \begin{table}[!htb]
%   \caption{Comparing effect of machine complexity}

%   \begin{minipage}{.5\linewidth}
%     \caption{Results for low complexity}
%     \centering
%       \begin{tabular}{|c|c|c|c|c|c|}
%         \hline
%         Model & $\mathcal{N}$ & $\mathcal{T}$ & Time(s) & Gap (\%) \\
%         \hline
%         Compact & ??? & ??? & ??? & ??? \\
%         DW & ??? & ??? & ??? & ??? \\
%         DW + PF & ??? & ??? & ??? & ??? \\
%         \hline
%       \end{tabular}
%   \end{minipage}
%   \begin{minipage}{.5\linewidth}
%     \centering
%       \caption{Results for high complexity}
%       \begin{tabular}{|c|c|c|c|c|c|}
%         \hline
%         Model & $\mathcal{N}$ & $\mathcal{T}$ & Time(s) & Gap (\%) \\
%         \hline
%         Compact & ??? & ??? & ??? & ??? \\
%         DW & ??? & ??? & ??? & ??? \\
%         DW + PF & ??? & ??? & ??? & ??? \\
%         \hline
%       \end{tabular}
%   \end{minipage} 
% \end{table}

% As expected, the decomposition approaches appear advantageous in comparison to the compact model when increasing the number of identical machines. On the other hand, having more machines increases the number of pricing problems, and longer time-horizons increase their difficulty, so the compact formulation seems better suited for these instances.

% An increase in machine complexity also increases the difficulty of the pricing problems....

@@

This article presented a MINLP for a general production-maintenance scheduling problem. 
Besides the compact model, we also developed a Dantzig-Wolfe reformulation, and an additional heuristic to aid with the difficult pricing problem.

    The compact model can quickly solve multiple instances to optimality, but it could not find feasible solutions in nearly $23\%$ of the instances. 
    Both decomposition approaches were generally an improvement, with heuristic pricing yielding the best results out of the three models.

    The heuristic should perform even better with additional work.
    Besides the comments at the end of Section~\ref{sec:heuristics}, we are considering taking better advantage of how fast the heuristic is.
    Our idea is doing multiple iterations of the heuristic with different production vectors, while adding benders-like optimality and feasibility cuts, which should provide significantly better columns.

  A different extended formulation seems promising, as it should reduce the number of costly pricing rounds. 
  The idea is to generate maintenance patterns and production patterns (patterns being a concrete assignment to the corresponding variables) in different pricing problems and combine them in the RMP. 
  This formulation needs more theory than the one presented in this paper, as it requires generation of column-and-row generation. 
  See~\cite{Simultaneous_column-and-row_generation} for more details on column-and-row generation.

  On the compact model side, more than one type of maintenance action can make the model more interesting. 
  It increases its difficulty, but it also makes it more realistic, as complete replacement of a component is usually not the only option. 
  The model can also become more general. 
  For example, there might be non-critical components that may be maintained while still allowing for some production of the machine.
   Another example is the production upper bound in Constraints\eqref{con:production_limit}, which might depend not only on the condition of individual components, but also on the joint condition of multiple components.
